\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.
% *** CITATION PACKAGES ***
\usepackage[backend=biber,
            hyperref=true,
            url=false,
            isbn=false,
            doi=false,
            backref=false,
            style=ieee,
            natbib=true,%compatibility aliases
            mincitenames=1,
            maxcitenames=1,
            citestyle=numeric-comp,
            sorting=nyt,%none
            block=none]{biblatex}
        
\renewcommand{\bibfont}{\small}
\addbibresource{references.bib}

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

%=======INPUT SETUP FILES=======
\input{includes/0-preamble}
% \input{0-macros.tex}
\input{includes/0-defs}

%\usepackage{titling}
\usepackage[colorinlistoftodos]{todonotes}

%=======U S E R  D E F I N E D  M A C R O S=======
% \newcommand{\probName}{mechanical search\xspace}
% \newcommand{\lowLevelName}{methods\xspace}
% \newcommand{\algoAbbr}{MS-TRC\xspace}
% \newcommand{\algo}{target retrieval in clutter\xspace}
% \newcommand{\Algo}{Target Retrieval in Clutter\xspace}

%=======U S E R  D E F I N E D  M A C R O S=======
% \newcommand{\probName}{mechanical search\xspace}
% \newcommand{\lowLevelName}{methods\xspace}
% \newcommand{\algoAbbr}{MS-TRC\xspace}
% \newcommand{\algo}{target retrieval in clutter\xspace}
% \newcommand{\Algo}{Target Retrieval in Clutter\xspace}

%=======DOC INFO=======
\title{\LARGE \bf
Kit-Net: Self-Supervised Learning to Kit \\Novel 3D Objects into Novel 3D Cavities
}

\author{Shivin Devgon$^{1}$, Jeffrey Ichnowski$^{1}$, Michael Danielczuk$^{1}$, Daniel S. Brown$^{1}$, Ashwin Balakrishna$^{1}$, \\
Shirin Joshi$^{2}$, Eduardo M. C. Rocha$^{2}$, Eugen Solowjow$^{2}$, Ken Goldberg$^{1}$ % <-this % stops a space
\thanks{$^{1}$The AUTOLAB at the University of California, Berkeley. %}%
%\thanks{
$^{2}$Siemens Research Lab, Berkeley, CA.
{\tt\small
  \{shivin302, jeffi, mdanielczuk, dsbrown, ashwin\_balakrishna\}\allowbreak @berkeley.edu,
  \{shirin.joshi, eduardo.moura\_cirilo\_rocha,
  eugen.solowjow\}\allowbreak @siemens.com,
  goldberg@berkeley.edu }
}%
}

\begin{document}

\maketitle
% \thispagestyle{empty}
% \pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In industrial part kitting, 3D objects are inserted into cavities for transportation or subsequent assembly. Kitting is a critical step in industrial transportation and assembly, as kitting can decrease downstream processing and handling times and enable lower storage and shipping costs.
% Adapting to varying object and cavity shapes, kitting can decrease  
We present Kit-Net, a framework for kitting previously unseen 3D objects into cavities given depth images of both the target cavity and an object held by a gripper in an unknown initial orientation. Kit-Net uses self-supervised deep learning and data-augmentation to train a CNN to robustly estimate 3D rotations between objects and matching concave or convex cavities using a large dataset of simulated depth images pairs. Kit-Net then uses the trained CNN to implement a controller to orient and position novel objects for insertion into novel prismatic and conformal 3D cavities. Experiments in simulation suggest that Kit-Net can orient objects to have a 98.9\,\% average intersection volume between the object mesh and that of the target cavity. Physical experiments with 3 industrial objects suggest that Kit-Net can successfully insert objects into cavities with a 63\,\% success rate while a baseline which restricts itself to 2D rotations succeeds only 18\,\% of the time. 

\end{abstract}

\input{includes/1-introduction}
\input{includes/2-related-work}
\input{includes/3-problem-statement}
\input{includes/4-methods}
\input{includes/5-simulation}
\input{includes/6-physical-experiments}
\input{includes/7-discussion}
% only need acks in cam ready
\input{includes/8-acknowledgement}


% \addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths % on the last page of the document manually. It shortens % the textheight of the last page by a suitable amount. % This command does not take effect until the next page % so it should come on the page before the last. Make % sure that you do not shorten the textheight too much.

%\balance
%=====================================
\renewcommand*{\bibfont}{\footnotesize}
% \renewcommand{\baselinestretch}{0.9} %only do this for refs if crunched for space
\printbibliography %for biblatex -- doesnt work with natbib
%=====================================
% only for generating the appendices.
% Include appendices in pdf
% \clearpage
% \input{includes/8-appendix}

\end{document}
